True versus apparent shapes of bow shocks and bow waves

### 2017-11-11 papers/Paper1/sec-thin-shell.tex
Start to describe Figs 13, 14 on true ancantoid shapes

The resulting shapes are shown in
Figure~\ref{fig:r-beta} for three different values of \(\beta\).  There is
a general tendency for the bows to be flatter and more open with
increasing \(\beta\), while at a given \(\beta\) it is the cantoid (black
lines) that is most open

>>>>

The shapes of the ancantoid bow shocks are shown in
Figure~\ref{fig:r-beta} for three different values of \(\beta\), and are
compared with the \CRW{} results for cantoids (dashed curves).  The
location of these shapes in the planitude--alatude plane is shown in
Figure~\ref{fig:ancantoid-Pi-lambda-true}, where the gray background
shading indicates the zones of different quadric classes, as in
\S~\ref{sec:conic}, Figures~\ref{fig:quadric-projection-continued}
and~\ref{fig:projected-R90-Rc-snapshots}.  The \(k=0\) ancantoid is
identical to the cantoid for \(\theta \le 90^\circ\) (\(z > 0\)), but is slightly
more swept back in the far wings.\footnote{%
  Due to the discontinuity in the inner wind density at
  \(theta = 90^\circ\) (see Fig.~\ref{fig:anisotropic-arrows}), there is a
  discontinuity in the second derivative of the bow shape.} %
Since the true planitude and alatude depend on \(R(\theta)\) only in the
range \(\theta = [0, 90^\circ]\), the cantoid and the \(k = 0\) ancantoid
behave identically in Figure~\ref{fig:ancantoid-Pi-lambda-true}.

There is a general tendency for the bows to be flatter and more open
with increasing \(\beta\) and decreasing \(k\), with the cantoid being
most open at a given \(\beta\).  All the models cluster close to the
diagonal \(\Lambda \simeq \Pi\) in the planitude--alatude plane, but with a tendency
for \(\Lambda > \Pi\) at higher anisotropy.  There is therefore a degeneracy
between \(\beta\) and \(k\) for higher values of \(\beta\).  The wilkinoid
shape, which corresponds to the \(\beta \to 0\) limit of the cantoids is
marked by a white plus symbol in
Figure~\ref{fig:ancantoid-Pi-lambda-true}, which lies in the prolate
ellipsoid region of the plane.
